Enzo: An Adaptive Mesh Refinement Code for Astrophysics

### 2013-06-07 numerical-chemistry.tex
Three minor changes to table:
 * H2 + D+ => HD + D+ has become H2 + D+ => HD + H+
 * Added H- + D => HD + e- which is in the code
 * Added D photoionization rate.

\begin{table}
\begin{center}
{\bfseries Collisional Processes}\\[1ex]
\begin{tabular}{llllllll}
(1) & H & + & e$^-$ & $\rightarrow$ & H$^+$ &+& 2e$^-$ \\
(2) & H$^+$ &+ &e$^-$ & $\rightarrow$ & H &+ &$\gamma$ \\
(3) & He &+& e$^-$ & $\rightarrow$ & He$^+$ &+& 2e$^-$  \\
(4) & He$^+$ &+& e$^-$ & $\rightarrow$ & He &+ &$\gamma$  \\
(5) & He$^{+}$ &+& e$^-$ & $\rightarrow$ & He$^{++}$ &+& 2$e^-$  \\
(6) & He$^{++}$ &+& e$^-$ & $\rightarrow$ & He$^+$ &+& $\gamma$ \\
\hline
(7) & H &+& e$^-$ &$\rightarrow$& H$^-$ &+& $\gamma$  \\
(8) & H$^-$ &+& H &$\rightarrow$ & H$_2$ & +& e$^-$ \\
(9) & H &+ &H$^+$ &$\rightarrow$ &H$_2^+$ &+ &$\gamma$ \\
(10) & H$_2^+$ &+ &H &$\rightarrow$ &$H_2$ &+ &$H^+$ \\
(11) & H$_2$ &+ &H$^+$ &$\rightarrow$ &H$_2^+$ & +& H \\
(12) & H$_2$ &+ &e$^-$ & $\rightarrow$ & 2H & + & e$^-$  \\
(13) & H$_2$ & + & H & $\rightarrow$ & 3H &   &      \\
(14) & H$^-$ & + & e$^-$ & $\rightarrow$ & H & + & 2e$^-$ \\
(15) & H$^-$ & + & H & $\rightarrow$ & 2H & + & e$^-$ \\ 
(16) & H$^-$ & + & H$^+$ & $\rightarrow$ & 2H & & \\
(17) & H$^-$ & + & H$^+$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(18) & H$_2^+$ & + & e$^-$ & $\rightarrow$ & 2H & & \\
(19) & H$_2^+$ & + & H$^-$ & $\rightarrow$ & H$_2$ & + & H  \\
(20) & 2H & + & H$_2$ & $\rightarrow$ & 2H$_2$ &  &   \\
(21) & 2H & + & H & $\rightarrow$ & H$_2$ & + & H  \\
(22) & H$_2$ & + & H$_2$ & $\rightarrow$ & H$_2$ & + & 2H  \\
(23) & 3H & & & $\rightarrow$ & H$_2$ & + & H \\
\hline
(24) & D & + & e$^-$ & $\rightarrow$ & D$^+$ &+& 2e$^-$ \\
(25) & D$^+$ &+ &e$^-$ & $\rightarrow$ & D &+ &$\gamma$ \\
(26) & H$^+$ &+ &D & $\rightarrow$ & H &+ &D$^+$ \\
(27) & H &+ &D$^+$ & $\rightarrow$ & H$^+$ &+ &D \\
(28) & H$_2$ &+ &D$^+$ & $\rightarrow$ & HD &+ &D$^+$ \\
(29) & HD &+ &H$^+$ & $\rightarrow$ & H$_2$ &+ &D$^+$ \\
(30) & H$_2$ &+ &D & $\rightarrow$ & HD &+ &H \\
(31) & HD &+ &H & $\rightarrow$ & H$_2$ &+ &D \\

@@

\begin{table}
\begin{center}
{\bfseries Radiative Processes}\\[1ex]
\begin{tabular}{llllllll}
(32) & H & + & $\gamma$ & $\rightarrow$ & H$^+$ & + & e$^-$ \\
(33) & He & + & $\gamma$ & $\rightarrow$ & He$^+$ & + & e$^-$ \\
(34) & He$^+$ & + & $\gamma$ & $\rightarrow$ & He$^{++}$ & + & e$^-$ \\
(35) & H$^-$ & + & $\gamma$ & $\rightarrow$ & H & + & e$^-$ \\
(36) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(37) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & H & + & H$^+$ \\
(38) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & 2H$^+$ & + & e$^-$ \\
(39) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^*$ & $\rightarrow$ & 2H \\
(40) & H$_2$ & + & $\gamma$ & $\rightarrow$ & 2H &  & 
\end{tabular}
\caption[]{Radiative processes solved in the \enzo\ nonequilibrium
primordial chemistry routines. \red{Missing rates for HD destruction/ionization?}}
\label{table.radiative}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
{\bfseries Collisional Processes}\\[1ex]
\begin{tabular}{llllllll}
(1) & H & + & e$^-$ & $\rightarrow$ & H$^+$ &+& 2e$^-$ \\
(2) & H$^+$ &+ &e$^-$ & $\rightarrow$ & H &+ &$\gamma$ \\
(3) & He &+& e$^-$ & $\rightarrow$ & He$^+$ &+& 2e$^-$  \\
(4) & He$^+$ &+& e$^-$ & $\rightarrow$ & He &+ &$\gamma$  \\
(5) & He$^{+}$ &+& e$^-$ & $\rightarrow$ & He$^{++}$ &+& 2$e^-$  \\
(6) & He$^{++}$ &+& e$^-$ & $\rightarrow$ & He$^+$ &+& $\gamma$ \\
\hline
(7) & H &+& e$^-$ &$\rightarrow$& H$^-$ &+& $\gamma$  \\
(8) & H$^-$ &+& H &$\rightarrow$ & H$_2$ & +& e$^-$ \\
(9) & H &+ &H$^+$ &$\rightarrow$ &H$_2^+$ &+ &$\gamma$ \\
(10) & H$_2^+$ &+ &H &$\rightarrow$ &$H_2$ &+ &$H^+$ \\
(11) & H$_2$ &+ &H$^+$ &$\rightarrow$ &H$_2^+$ & +& H \\
(12) & H$_2$ &+ &e$^-$ & $\rightarrow$ & 2H & + & e$^-$  \\
(13) & H$_2$ & + & H & $\rightarrow$ & 3H &   &      \\
(14) & H$^-$ & + & e$^-$ & $\rightarrow$ & H & + & 2e$^-$ \\
(15) & H$^-$ & + & H & $\rightarrow$ & 2H & + & e$^-$ \\ 
(16) & H$^-$ & + & H$^+$ & $\rightarrow$ & 2H & & \\
(17) & H$^-$ & + & H$^+$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(18) & H$_2^+$ & + & e$^-$ & $\rightarrow$ & 2H & & \\
(19) & H$_2^+$ & + & H$^-$ & $\rightarrow$ & H$_2$ & + & H  \\
(20) & 2H & + & H$_2$ & $\rightarrow$ & 2H$_2$ &  &   \\
(21) & 2H & + & H & $\rightarrow$ & H$_2$ & + & H  \\
(22) & H$_2$ & + & H$_2$ & $\rightarrow$ & H$_2$ & + & 2H  \\
(23) & 3H & & & $\rightarrow$ & H$_2$ & + & H \\
\hline
(24) & D & + & e$^-$ & $\rightarrow$ & D$^+$ &+& 2e$^-$ \\
(25) & D$^+$ &+ &e$^-$ & $\rightarrow$ & D &+ &$\gamma$ \\
(26) & H$^+$ &+ &D & $\rightarrow$ & H &+ &D$^+$ \\
(27) & H &+ &D$^+$ & $\rightarrow$ & H$^+$ &+ &D \\
(28) & H$_2$ &+ &D$^+$ & $\rightarrow$ & HD &+ &H$^+$ \\
(29) & HD &+ &H$^+$ & $\rightarrow$ & H$_2$ &+ &D$^+$ \\
(30) & H$_2$ &+ &D & $\rightarrow$ & HD &+ &H \\
(31) & HD &+ &H & $\rightarrow$ & H$_2$ &+ &D \\
(32) & H$^-$ &+ &D & $\rightarrow$ & HD &+ &e$^-$ \\

@@

\begin{table}
\begin{center}
{\bfseries Radiative Processes}\\[1ex]
\begin{tabular}{llllllll}
(33) & H & + & $\gamma$ & $\rightarrow$ & H$^+$ & + & e$^-$ \\
(34) & He & + & $\gamma$ & $\rightarrow$ & He$^+$ & + & e$^-$ \\
(35) & He$^+$ & + & $\gamma$ & $\rightarrow$ & He$^{++}$ & + & e$^-$ \\
(36) & H$^-$ & + & $\gamma$ & $\rightarrow$ & H & + & e$^-$ \\
(37) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^+$ & + & e$^-$ \\
(38) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & H & + & H$^+$ \\
(39) & H$_2^+$ & + & $\gamma$ & $\rightarrow$ & 2H$^+$ & + & e$^-$ \\
(40) & H$_2$ & + & $\gamma$ & $\rightarrow$ & H$_2^*$ & $\rightarrow$ & 2H \\
(41) & H$_2$ & + & $\gamma$ & $\rightarrow$ & 2H &  & \\
(42) & D & + & $\gamma$ & $\rightarrow$ & D$^+$ & + & e$^-$ \\
\end{tabular}
\caption[]{Radiative processes solved in the \enzo\ nonequilibrium
primordial chemistry routines. \red{Missing rates for HD destruction/ionization?}}
\label{table.radiative}
\end{center}
\end{table}
